### 2018-02-23 paper/sections/5_file-systems.tex
paper: fix title and minor typos
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>
paper: add acknowledgements
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\subsection{Using Cache Management Policies for Load Balancing}
\label{sec:using-cache-management-policies-for-load-balancing}
\begin{figure}[t]
\noindent\includegraphics[width=0.5\textwidth]{figures/trace-atime.png}\\
\caption{File system metadata reads for a Lustre trace collected at LANL. The
vertical lines are the results of running the pattern detection algorithm
used for cache management in Section~\S\ref{sec:dom-specific}. File system
cases are in
Section~\S\ref{sec:using-cache-management-policies-for-load-balancing}.
\label{fig:trace-atime}}
\end{figure}
%A file system that
%load balances metadata across a cluster of servers could use the same pattern
%detection to make migration decisions, such as avoiding migration when the
%workload is accessing the same subset of keys or keeping groups of accesses
%local to a server.

@@

\begin{itemize}

  \item QoS: when to move clients, where to move clients, how much of the
reservation to move. We could use Mantle to implement something like the
reservation algorithms based on utilization and period in
Fahrrad~\cite{povzner_horizon_2010} to achieve better guarantees without
sacrificing performance.

  \item Scheduling: when to yield computation cycles to another process, how
much of a resource to allocate. We could use Mantle to implement the
fairness/priority models used in the Mesos~\cite{hindman_mesos_2011} ``how
many" policies.

  \item Batching: how many operations to group together, when to send large
batches of updates. We could use Mantle to implement pathname leases from
IndexFS~\cite{ren:sc2014-indexfs} or the capabilities from
CephFS.

  \item Prefetching: how much to prefetch, how to select data.  We could use
Mantle to implement forward/backward/stride detection algorithms for
prefetching in RAID arrays or something more complicated, like the time series
algorithms for adaptive I/O prefetching from~\cite{tran:sc01-arima}.

\end{itemize}

>>>>

\subsection{Using Cache Management Policies for Load Balancing}
\label{sec:using-cache-management-policies-for-load-balancing}
\begin{figure}[t]
\noindent\includegraphics[width=0.5\textwidth]{figures/trace-atime.png}\\
\caption{File system metadata reads for a Lustre trace collected at LANL. The
vertical lines are the results of running the pattern detection algorithm
used for cache management in Section~\S\ref{sec:dom-specific}. File system
use cases are in
Section~\S\ref{sec:using-cache-management-policies-for-load-balancing}.
\label{fig:trace-atime}}
\end{figure}
%A file system that
%load balances metadata across a cluster of servers could use the same pattern
%detection to make migration decisions, such as avoiding migration when the
%workload is accessing the same subset of keys or keeping groups of accesses
%local to a server.

@@

\textbf{QoS}: when to move clients, where to move clients, how much of the
reservation to move. We could use Mantle to implement something like the
reservation algorithms based on utilization and period in
Fahrrad~\cite{povzner_horizon_2010} to achieve better guarantees without
sacrificing performance.

\textbf{Scheduling}: when to yield computation cycles to another process, how
much of a resource to allocate. We could use Mantle to implement the
fairness/priority models used in the Mesos~\cite{hindman_mesos_2011} ``how
many" policies.

\textbf{Batching}: how many operations to group together, when to send large
batches of updates. We could use Mantle to implement pathname leases from
IndexFS~\cite{ren:sc2014-indexfs} or the capabilities from
CephFS.

\textbf{Prefetching}: how much to prefetch, how to select data.  We could use
Mantle to implement forward/backward/stride detection algorithms for
prefetching in RAID arrays or something more complicated, like the time series
algorithms for adaptive I/O prefetching from~\cite{tran:sc01-arima}.

### 2018-02-23 paper/sections/6_conclusion.tex
paper: camera-ready format; squeeze to 10 pgs
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>
paper: add acknowledgements
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

State-of-the-art distributed file systems partition write-heavy workloads and
replicate read-heavy workloads, similar to the approach we are advocating here.
IndexFS~\cite{ren:sc2014-indexfs} partitions directories and clients write to
different partitions by grabbing leases and caching ancestor metadata for path
traversal. ShardFS~\cite{xiao:socc15-shardfs} takes the replication approach to
the extreme by copying all directory state to all nodes.
CephFS~\cite{weil:sc2004-dyn-metadata, weil:osdi2006-ceph} employs both
techniques to a lesser extent; directories can be replicated or sharded but the
caching and replication policies are controlled with tunable parameters.  These
systems still need to be tuned by hand with {\it ad-hoc} policies designed for
specific applications.  Setting policies for migrations is arguably more
difficult than adding the migration mechanisms themselves.  For example,
IndexFS/CephFS use the GIGA+~\cite{patil:fast2011-giga} technique for
partitioning directories at a \emph{predefined} threshold. Mantle makes headway
in this space by providing a framework for exploring these policies, but does
not attempt anything more sophisticated ({\it e.g.}, machine learning) to
create these policies.

@@

Data management encompasses a wide range of techniques that vary by application
and storage system.  Yet, the techniques require policies that shape the
decision making and finding the best policies is a difficult, multi-dimensional
problem.  We iterate to a custom solution for our target application that uses
workload access patterns to size its caches. Without tuning or parameter
sweeps, our solution saves memory without sacrificing performance for a variety
of initial conditions, including the scale, duration, configuration, and
hardware of the simulation. More importantly, rather than attempting to
construct a single, complex policy that works for a variety of scenarios, we
instead use the Mantle framework to enable software-defined storage systems to
flexibly change policies as the workload changes.  We also observe that many of
the primitives and strategies have enough in common with data management in
file systems that they both can be expressed with similar semantics.

This lays the foundation for future work, where we will focus on formalizing a
collection of general data management policies that can be used across
applications and storage systems.  The value of such a collection eases the
burden of policy development and paves the way for automated solutions such as
(1) adaptable policies that switch to new strategies when the current strategy
behaves poorly ({\it e.g.}, thrashing, making no progress, etc.), and (2)
policy generation, where new policies are constructed by examining the
collection of existing policies.  Ultimately, we hope that this automation
enables control of policies by machines instead of administrators.

>>>>

State-of-the-art distributed file systems partition write-heavy workloads and
replicate read-heavy workloads, similar to the approach we are advocating here.
IndexFS~\cite{ren:sc2014-indexfs} partitions directories and clients write to
different partitions by grabbing leases and caching ancestor metadata for path
traversal. ShardFS~\cite{xiao:socc15-shardfs} takes the replication approach to
the extreme by copying all directory state to all nodes.
CephFS~\cite{weil:sc2004-dyn-metadata, weil:osdi2006-ceph} employs both
techniques to a lesser extent.  These systems still need to be tuned by hand
with {\it ad-hoc} policies designed for specific applications.  For example,
IndexFS and CephFS partition directories at \emph{predefined} thresholds,
which are difficult to define at the beginning of the job. Mantle makes headway
in this space by providing a framework for exploring these policies, but does
not attempt anything more sophisticated ({\it e.g.}, machine learning) to
create these policies.

@@

Data management encompasses a wide range of techniques that vary by application
and storage system.  Yet, the techniques require policies that shape the
decision making and finding the best policies is a difficult, multi-dimensional
problem.  We iterate to a custom solution for our target application that uses
workload access patterns to size its caches. Without tuning or parameter
sweeps, our solution saves memory without sacrificing performance for a variety
of initial conditions. More importantly, rather than attempting to
construct a single, complex policy that works for a variety of scenarios, we
instead use the Mantle framework to enable software-defined storage systems to
flexibly change policies as the workload changes.  We also observe that many of
the primitives and strategies have enough in common with data management in
file systems that they both can be expressed with similar semantics.

This lays the foundation for future work, where we will focus on formalizing a
collection of general data management policies that can be used across
applications and storage systems.  This eases the
burden of policy development and paves the way for automated solutions such as
(1) adaptable policies that switch to new strategies when the current strategy
behaves poorly ({\it e.g.}, thrashing), and (2)
policy generation, where new policies are constructed by examining the
collection of existing policies.  We hope that this automation
enables control of policies by machines instead of administrators.
